\section{Executive Summary}

PurpleMarket is a web application that will connect students, staff, and faculty from San Francisco State together via a virtual marketplace. In this marketplace, they will be able to communicate with each other, as well as buy and sell products on a user to user basis. There will be no intermediate and no surprises. What one user posts will be verified and will be exactly what is sold to another user. With this in mind we hope to create a safer, open community at San Francisco State, while also providing our users with a more convenient way to shop. The value of PurpleMarket is in its ability to provide an experience custom tailored to people associated with San Francisco State. Our vision is to provide a marketplace that facilitate the ability to sell and purchase the types of items and/or services that are most important to our users. 

PurpleMarket plans to be easy to navigate, and easy on the eyes. There isn’t any clutter which makes the site much more presentable to our users. Our users are presented with a clean design that will make it much easier for users to navigate our site to find exactly what they are looking for. If they have any trouble at all finding their specific product, they are able to narrow their search in three ways. The first method to finding their desired product is by browsing different categories. By providing categories that our users are most interested in, our users will be able to more easily sell or find the products that they want. The second method will be a simple and easy to use search that would allow the user to type specific titles, names, or descriptions where the user will be presented with the results of the search. Specific to the academic environment, the final method for finding a product is by finding products that are associated with a particular course.  Once a user finds what they are looking for they can sign up and create a PurpleMarket account that will allow them to communicate with the user that listed the product directly on our site and the rest is history. So what about listing products?  Any verified user who opens an account will be able to list a product. Finally, PurpleMarket will be able to facilitate on-campus meetings between buyer and seller, which simplifies the transaction experience.

Our team of passionate San Francisco State students know the frustrations of navigating online classifieds and the unique needs of the people associated with the school.  It is because of this that we are exceptionally equipped to understand the San Francisco State community and provide them with the experience that they desire.