\section{List of Functional Requirements}

\begin{description}[font=\itshape]
\item[Unregistered User]\hfill
    \begin{enumerate}
        \item Unregistered users shall be able to search the site for certain posts.\\This function is needed to narrow down posts that fit what the user is looking for.
        \item Unregistered users shall be able to filter search results.\\This function is needed to narrow down posts that fit what the user is looking for.
        \item Unregistered users shall be able to register for an account.
        \item Unregistered users shall click on a post\\Unregistered user can click on a post, even though he doesn’t have an account.
        \item Unregistered users shall not send contact the seller\\They can’t send a message unless they have an account 
    \end{enumerate}
\item[Registered User]\hfill
    \begin{enumerate}
    	\setcounter{enumi}{5}
        \item Registered users shall be able to do everything an unregistered user can do.
        \item Registered users shall be able to create posts.\\The user needs this function in order to sell their products.
        \item Registered users shall be able to get in contact with the poster/seller.\\Either contact information is available or there’s a messaging chat box on the site. This function is needed for transactions to take place between users. 
		\item Registered users shall be able to edit and correct and/or delete their own post after it was submitted.\\If there is some mistake on the original post, then users should be able to edit their post. If suddenly the user cannot offer the product anymore, then the user shall be able to delete the post.
		\item Registered users shall be able to report violations of terms of service of another user.\\If the user doesn’t get the product as it was displayed or described, then they should be able to report the selling user. If the selling user gets paid with fake money or they were robbed at their transaction meetup, then the user should be able to report the buying user.
		\item Registered users shall be able to login to their account.\\They need to login to do their admin duties of approving posts and doing regular things like buying and selling items.
		\item Registered users shall be able to logout of their account.\\They need to logout to secure their account from anyone else using the same computer.
		\item Registered users shall be able to request/reset their password if they forgot.\\Users shall be able to access their account they made so password reset will be provided if they forgot their password.
		\item Registered users shall be able to leave reviews of other users regarding completed transactions.\\They shall be able to leave a review of transaction experience of the other party in a transaction.
		\item Registered users shall be able to propose meeting locations or modify location proposals to complete transactions.
		\item Registered users shall be able to inspect their transaction history.
    \end{enumerate}
\item[Admin]\hfill
    \begin{enumerate}
    	\setcounter{enumi}{16}
        \item Admins shall be able to do everything a registered user can do.
        \item Admins shall be able to delete and edit posts done by any user.\\If admins find any posts that do not follow terms of service, they should be able to delete or edit the offending content.
        \item Admins shall be able to contact any user.\\The admins should be able to contact any user for administrative purposes (i.e. warnings).
        \item Admins shall be able to ban users.\\Admins should be able to ban repeat offenders from the platform.
        \item Admins shall be able to approve posts.\\Admins should be able to approve posts waiting for approval.
        \item Admins shall be able to inspect any user's transaction history.
    \end{enumerate}

\end{description}
