\section{Architecture}

\subsection{DB Organization}

{\large user table}
\begin{enumerate}
\item user\_id: unique user identification
\item user\_fname: user's first name
\item user\_lname: user's last name
\item user\_email: user's email
\item user\_type: user type (e.g. admin, staff, faculty, student)
\item user\_password: user's password
\end{enumerate}%
%
{\large item}
\begin{enumerate}
\item item\_id: unique item identification
\item item\_created: time that posting was created
\item item\_category: item's category
\item item\_seller\_id: user id of seller
\item item\_price: price of item
\item item\_name: name of item
\item item\_desc: description of item
\item item\_pic: picture of item (path)
\item item\_course: course associated with item
\item item\_golive\_time: time of approval 
\end{enumerate}%
%
{\large category}
\begin{enumerate}
\item category\_id: unique category identification
\item category\_name: name of category
\end{enumerate}
%
{\large session}
\begin{enumerate}
\item session\_id: unique session identification
\item session\_user: user associated with session
\item session\_expires: session expiration time
\item session\_data: session data
\end{enumerate}%
%
{\large message}
\begin{enumerate}
\item msg\_id: unique message identification
\item msg\_sender: sender of message
\item msg\_recipient: recipient of message
\item msg\_item: item associated with message
\item msg\_meet\_time: proposed meeting time
\item msg\_location: proposed meeting location
\item msg\_contactinfo: contact information of sender
\item msg\_body: body of message
\item msg\_timestamp: timestamp of message
\end{enumerate}%
%
{\large review}
\begin{enumerate}
\item review\_id: unique review identification
\item review\_item: item associated with review
\item review\_recipient: user id of recipient of review
\item review\_contributor: user id of the contributor the review
\item review\_rating: rating of review recipient
\item review\_body: body of review
\item review\_timestamp: time of review
\end{enumerate}%

\subsection{Media Storage}
User uploaded images will be stored in an AWS S3 bucket. The S3 bucket will give read-only access to the public. We want users who haven’t created accounts yet to be able to view some posts with their respective images while securing write permissions to registered users only. We will use the S3 AWS SDK API for certified users who created accounts to upload images to the S3 bucket when creating a post.

\subsection{Search/filter architecture and implementation}
\begin{enumerate}
\item Database queries shall be utilized for all search items for the user.
\item Item names and descriptions shall be utilized for keyword searches.
\item Item categories shall be browsable and searchable.
\item Course materials shall be searchable by course name.
\item Search results shall be sortable by price, post age, category, item name, or seller username.
\end{enumerate}

\subsection{Team 8 APIs}
None

\subsection{Algorithms or Processing}
None

\subsection{SW Tool and Framework Changes}
S3 storage for image storage. (seeking approval)
