\section{Key Risks}

\subsection{Skills Risks}
\begin{itemize}
\item Most of the team has very little experience in deploying a project of this scale on the cloud.  Local development environments may be quite different from the cloud production environment, which requires a set of skills that have not been practiced thoroughly.
\item The skill level for various frameworks is varied from team member to team member.
\end{itemize}

\begin{itemize}
\item Schedule substantial time for research and trial-and-error.
\item Promote collaboration between team members so that the entire team can benefit from each member's strengths.
\end{itemize}

\subsection{Schedule Risks}
\begin{itemize}
\item The scope of the project is substantial compared to the limited time we have.\\
This is a risk in the sense it is not certain whether we are able to successfully complete the entire website as required.
\item With varied course loads between students, each student is available at different times throughout each week.
\end{itemize}

\begin{itemize}
\item We may reduce the scope of the project and focus on completing highest priority items first.
\item Divide the work amongst team members as much as possible and delegate according to each students' needs.
\item Create deadlines with contingency plans in place to ensure that work gets completed on-time.
\end{itemize}

\subsection{Technical Risks}
\begin{itemize}
\item Due to the scale of the project and the amount of new technologies involved there is a chance that as a team we may not be able to accomplish something successfully due to lack of expertise.
\item Breaking of systems due to lack of expertise and/or mistakes.
\end{itemize}

\begin{itemize}
\item We plan to follow the method of practice and learn until we succeed!
\item Use tutorials online and follow articles and forums which will help us accomplish our desired output.
\item Try to simplify our project as much as possible to reduce the need for too many new technologies.
\item Maintain strict controls over each branch of code and the server to reduce the chance of mistakes.
\end{itemize}

\subsection{Teamwork Risks}
\begin{itemize}
\item There is a chance of conflict amongst team members where some members might think they do more work than others.
\end{itemize}

\begin{itemize}
\item Use project management tools like Trello to track tasks amongst team members for efficient planning.
\item Ensure that all team leads divide work efficiently.
\end{itemize}

\subsection{Legal/Content Risks}
None at the moment.